Verifying Demonstrations

### 2020-07-03 paper/DB-Schnorr-UWB.tex
Briefly explains Singh et al.'s paper

We will provide two versions of the protocol.
In the first (\cref{DB-Schnorr-UWB}), we will assume that we can send as many 
bits in parallel as we like.
This is a reasonable assumption thanks to the results of \textcite{UWBPR}.

@@

  If the adversary \(\Prompt\)s:
  The verifier will check that \(R' = g^{s_i} A'^{c_i}\), where \(A'\) is the 
  \enquote{public key}\footnote{%
    In Schnorr's original protocol this was a public key.
    In our more general use, it is the value for which the adversary wants to 
    prove knowledge of a discrete logarithm.
  } of the adversary.
  Now, \(g^{s_i} A'^{c_i} = g^{\rho - c_i \alpha} (g^{\alpha'})^{c_i} = g^{\rho 
  - c_i \alpha + c_i \alpha'}\).
  If \(R' = R = g^\rho\), chosen by the prover, then the verifier will only 
  accept if \(\alpha = \alpha'\), the probability for which is 
  \(\frac{1}{q^2}\).
  If \(R' = g^{\rho'}\), chosen by the adversary, then the verifier accepts 
  with probability \(\Pr[\rho' - c_i \alpha' = \rho - c_i' \alpha] = 
  \frac{1}{q}\).

>>>>

We will provide two versions of the protocol.
In the first (\cref{DB-Schnorr-UWB}), we will assume that we can send as many 
bits in parallel as we like.
This is a reasonable assumption thanks to the results of \textcite{UWBPR}, we 
briefly explain why.
\Ic{DBMF} adversary can listen in on the communications.
Each symbol of the communication is encoded using signal pulses.
However, such an encoded symbol can usually be inferred \emph{before} all 
pulses are received.
Before the contribution of \citeauthor{UWBPR}, the only countermeasure to this 
attack was to make the symbols short, \ie to send one bit at a time.
\Textcite{UWBPR} use a symmetric key, shared between prover and verifier, to 
scramble the pulses and hence the symbols.
This way, the \ac{DBMF} adversary cannot infer an incoming symbol in advance, 
and thus cannot start relaying the symbol in advance either.
The prover and verifier, on the other hand, can do this since they have the 
symmetric key.
Consequently they must have mutual trust, so \ac{DBDF} cannot happen by 
assumption.

@@

  If the adversary \(\Prompt\)s:
  The verifier will check that \(R' = g^{s_i} {A'}^{c_i}\), where \(A'\) is the 
  \enquote{public key}\footnote{%
    In Schnorr's original protocol this was a public key.
    In our more general use, it is the value for which the adversary wants to 
    prove knowledge of a discrete logarithm.
  } of the adversary.
  Now, \(g^{s_i} {A'}^{c_i} = g^{\rho - c_i \alpha} (g^{\alpha'})^{c_i} = 
  g^{\rho - c_i \alpha + c_i \alpha'}\).
  If \(R' = R = g^\rho\), chosen by the prover, then the verifier will only 
  accept if \(\alpha = \alpha'\), the probability for which is 
  \(\frac{1}{q^2}\).
  If \(R' = g^{\rho'}\), chosen by the adversary, then the verifier accepts 
  with probability \(\Pr[\rho' - c_i \alpha' = \rho - c_i' \alpha] = 
  \frac{1}{q}\).
